Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-07-19 manuscript.Rmd
Updating repo

articles.df$exp.175 <- exp.175
articles.df$exp.07  <- exp.07

ggplot(articles.df, aes(Year, CumSum, group =1)) + 
    theme_bw() + 
    geom_point(colour=cp[2], size = 3, alpha=.80) +
    theme(axis.text.x = element_text(size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Articles") + 
    scale_x_continuous(breaks=seq(1989, 2015, 8)) +
    #scale_y_continuous(breaks = c(seq(0, 2200, 250)), limits= c(500, 2100)) +
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75)) + 
    geom_line(aes(Year, exp.07), colour = cp[4]) +
    geom_line(aes(Year, exp.175), colour = cp[3]) +
    geom_smooth(method = "lm", colour = cp[1])

tail(articles.df)

head(articles.df)

exp.175 <- c(737, rep(NA, 24))

for(i in 2:25){
       exp.175[i] <- exp.175[i-1] + exp.175[i-1]*.175
 }

articles.df$exp.175 <- exp.175

@@

>>>>

exp.171 <- c(737, rep(NA, 24))
for(i in 2:25){
       exp.171[i] <- exp.171[i-1] + exp.171[i-1]*.171
    }

articles.df$exp.175 <- exp.175
articles.df$exp.07  <- exp.07
articles.df$exp.171 <- exp.171

ggplot(articles.df, aes(Year, exp.171, group =1)) + 
    theme_bw() + 
    geom_point(colour=cp[2], size = 3, alpha=.80) +
    geom_line(colour=cp[2]) + 
    theme(axis.text.x = element_text(size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Articles") + 
    scale_x_continuous(breaks=seq(1989, 2015, 8)) +
    #scale_y_continuous(breaks = c(seq(0, 2200, 250)), limits= c(500, 2100)) +
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75)) +
    geom_line(aes(Year, CumSum), colour = cp[3]) +
    geom_point(aes(Year, CumSum), colour = cp[3])

@@

n_authors_grouped <- n_authors %>%
    mutate(n = ifelse(n >= 4, 4, n)) %>%
    group_by(pubYear) %>%
    mutate(n.year = n()) %>%
    group_by(pubYear, n) %>%
    summarize(N =  n()) %>%
    group_by(pubYear) %>%
    mutate(N.year.overall = sum(N)) %>%
    mutate(N.percent = (N/N.year.overall)*100)

ggplot(n_authors_grouped, aes(pubYear, N.percent, group = n, colour = as.factor(n))) + geom_line(size = 1.5) + 
    scale_colour_manual(values = cp) +
    labs(colour = "Number of Authors") + 
    ylim(c(0,100)) + 
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75), 
          legend.position = "bottom") +
    theme(axis.text.x = element_text(size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10))
